*Salmonella* Environmental Persistence Informs Management Relevant to Avian and Public Health

### 2023-04-26 5. Manuscript/Manuscript.qmd
Working update

@@

![Positive Salmonella Samples by Type and
Date](images/Picnic_Table_PosSamp-05.png) Positive *Salmonella* Samples
by Sample Type and Date

![Positive *Salmonella* Samples by Quadrant and
Date](images/Picnic_Table_Quad-02.png)

@@

![Positive *Salmonella* Samples by feeder type and
date.](images/Feeder_PA.png)

>>>>

Statistical analysis was conducted on both datasets, Picnic Table Data
and Feeder Data, utilizing RStudio "Cherry Blossom" (2023-03-09).
Analysis for both datasets were evaluated utilizing a linear regression
model.

@@

![Positive Salmonella Samples by Type and
Date](images/Picnic_Table_PosSamp-05.png)***Figure 1.*** Positive
*Salmonella* Samples by Sample Type and Date

![***Figure 2.*** Positive *Salmonella* Samples by Quadrant and
Date](images/Picnic_Table_Quad-02.png)

@@

![***Figure 3.*** Positive *Salmonella* Samples by feeder type and
date.](images/Feeder_PA.png)
